Modeling thermal dust emission in the {\it PLANCK} 2015 release maps

### 2015-06-21 ms.tex
remove color from Table 1

\usepackage[dvipdf]{epsfig} 
\usepackage[dvips]{rotating}
\usepackage{subfigure}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{xcolor}

@@

\begin{center}
\begin{deluxetable*}{ccccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{8} 
\tablewidth{0pc} 
\tablecaption{\label{table:offs} Input Map Properties \& Pre-processing (2015 release)} 
\tablehead{
\colhead{$\nu$ (GHz)} &
\colhead{Instrument(s)} &
\colhead{Offset ($K_{CMB}$)} & 
\colhead{Dipole ($K_{CMB}$)} & 
\colhead{$s_{857,\nu}$$\times$$u_{\nu}$} &
\colhead{$\sigma_{s_{857,\nu}}$$\times$$u_{\nu}$} &
\colhead{$n_{\nu}$} ($K_{CMB}$) &
\colhead{$c_{\nu}$} &
\colhead{FWHM ($'$)}
}
\startdata
100  & \PLANCK~HFI & \textcolor{red}{9.65$\times$10$^{-6}$$\pm$4.00$\times$10$^{-7}$} & \textcolor{red}{1.77$\times$10$^{-6}$}    & \textcolor{red}{1.63$\times$10$^{-3}$} & \textcolor{red}{3.25$\times$10$^{-5}$}  & \textcolor{red}{5.06$\times$10$^{-5}$} & \textcolor{red}{0.0009} & \textcolor{red}{9.68}   \\
143  & \PLANCK~HFI & \textcolor{red}{2.34$\times$10$^{-5}$$\pm$7.72$\times$10$^{-7}$} & \textcolor{red}{1.48$\times$10$^{-6}$}    & \textcolor{red}{4.79$\times$10$^{-3}$} & \textcolor{red}{9.58$\times$10$^{-5}$}  & \textcolor{red}{2.18$\times$10$^{-5}$} & \textcolor{red}{0.0007} & \textcolor{red}{7.30}   \\
217  & \PLANCK~HFI & \textcolor{red}{6.68$\times$10$^{-5}$$\pm$2.70$\times$10$^{-6}$} & \textcolor{red}{9.05$\times$10$^{-6}$}    & \textcolor{red}{2.17$\times$10$^{-2}$} & \textcolor{red}{4.35$\times$10$^{-4}$}  & \textcolor{red}{3.06$\times$10$^{-5}$} & \textcolor{red}{0.0016} & \textcolor{red}{5.02}   \\
353  & \PLANCK~HFI & \textcolor{red}{4.01$\times$10$^{-4}$$\pm$2.06$\times$10$^{-5}$} & \textcolor{red}{3.09$\times$10$^{-5}$}    & \textcolor{red}{9.90$\times$10$^{-2}$} & \textcolor{red}{1.98$\times$10$^{-3}$}  & \textcolor{red}{1.01$\times$10$^{-4}$} & \textcolor{red}{0.0078} & \textcolor{red}{4.94}   \\
     &             & Offset (MJy/sr)                                                  & Dipole (MJy/sr)                           & $s_{857,\nu}$                          & $\sigma_{s_{857,\nu}}$                  & $n_{\nu}$ (MJy/sr)                     &                         &          \\ \cline{3-7} \\ [-2ex]
545  & \PLANCK~HFI & \textcolor{red}{3.07$\times$10$^{-1}$$\pm$2.01$\times$10$^{-2}$} & \textcolor{red}{1.00$\times$10$^{-2}$}    & \textcolor{red}{3.36$\times$10$^{-1}$} & \textcolor{red}{6.71$\times$10$^{-3}$}  & \textcolor{red}{0.031}                 & \textcolor{red}{0.061}  & \textcolor{red}{4.83}   \\
857  & \PLANCK~HFI & \textcolor{red}{4.72$\times$10$^{-1}$$\pm$6.00$\times$10$^{-2}$} & -                                         & \textcolor{blue}{1.0}                  & \textcolor{blue}{2.0$\times$10$^{-2}$}  & \textcolor{red}{0.028}                 & \textcolor{red}{0.064}  & \textcolor{red}{4.64}   \\
1250 & DIRBE       & \textcolor{red}{7.04$\times$10$^{-2}$$\pm$1.19$\times$10$^{-1}$} & -                                         & \textcolor{red}{2.05}                  & \textcolor{red}{4.10$\times$10$^{-2}$}  & \textcolor{blue}{0.42}                 & \textcolor{blue}{0.10}  & \textcolor{blue}{42}    \\
2141 & DIRBE       & \textcolor{red}{9.94$\times$10$^{-2}$$\pm$1.53$\times$10$^{-1}$} & -                                         & \textcolor{red}{2.65}                  & \textcolor{red}{5.29$\times$10$^{-2}$}  & \textcolor{blue}{0.79}                 & \textcolor{blue}{0.10}  & \textcolor{blue}{42}    \\
3000 & DIRBE/\IRAS & \textcolor{blue}{0.0$\pm$4.3$\times$10$^{-2}$}                   & -                                         & \textcolor{red}{1.30}                  & \textcolor{red}{2.60$\times$10$^{-2}$}  & \textcolor{blue}{0.06}                 & \textcolor{blue}{0.10}  & \ \textcolor{blue}{6.1}
\enddata
\end{deluxetable*}
\end{center}

>>>>

\usepackage[dvipdf]{epsfig} 
\usepackage[dvips]{rotating}
\usepackage{subfigure}
\usepackage{mathrsfs}
\usepackage{amsmath}

@@

\begin{center}
\begin{deluxetable*}{ccccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{8} 
\tablewidth{0pc} 
\tablecaption{\label{table:offs} Input Map Properties \& Pre-processing (2015 release)} 
\tablehead{
\colhead{$\nu$ (GHz)} &
\colhead{Instrument(s)} &
\colhead{Offset ($K_{CMB}$)} & 
\colhead{Dipole ($K_{CMB}$)} & 
\colhead{$s_{857,\nu}$$\times$$u_{\nu}$} &
\colhead{$\sigma_{s_{857,\nu}}$$\times$$u_{\nu}$} &
\colhead{$n_{\nu}$} ($K_{CMB}$) &
\colhead{$c_{\nu}$} &
\colhead{FWHM ($'$)}
}
\startdata
100  & \PLANCK~HFI & 9.65$\times$10$^{-6}$$\pm$4.00$\times$10$^{-7}$ & 1.77$\times$10$^{-6}$    & 1.63$\times$10$^{-3}$ & 3.25$\times$10$^{-5}$  & 5.06$\times$10$^{-5}$ & 0.0009 & 9.68   \\
143  & \PLANCK~HFI & 2.34$\times$10$^{-5}$$\pm$7.72$\times$10$^{-7}$ & 1.48$\times$10$^{-6}$    & 4.79$\times$10$^{-3}$ & 9.58$\times$10$^{-5}$  & 2.18$\times$10$^{-5}$ & 0.0007 & 7.30   \\
217  & \PLANCK~HFI & 6.68$\times$10$^{-5}$$\pm$2.70$\times$10$^{-6}$ & 9.05$\times$10$^{-6}$    & 2.17$\times$10$^{-2}$ & 4.35$\times$10$^{-4}$  & 3.06$\times$10$^{-5}$ & 0.0016 & 5.02   \\
353  & \PLANCK~HFI & 4.01$\times$10$^{-4}$$\pm$2.06$\times$10$^{-5}$ & 3.09$\times$10$^{-5}$    & 9.90$\times$10$^{-2}$ & 1.98$\times$10$^{-3}$  & 1.01$\times$10$^{-4}$ & 0.0078 & 4.94   \\
     &             & Offset (MJy/sr)                                 & Dipole (MJy/sr)          & $s_{857,\nu}$         & $\sigma_{s_{857,\nu}}$ & $n_{\nu}$ (MJy/sr)    &        &        \\ \cline{3-7} \\ [-2ex]
545  & \PLANCK~HFI & 3.07$\times$10$^{-1}$$\pm$2.01$\times$10$^{-2}$ & 1.00$\times$10$^{-2}$    & 3.36$\times$10$^{-1}$ & 6.71$\times$10$^{-3}$  & 0.031                 & 0.061  & 4.83   \\
857  & \PLANCK~HFI & 4.72$\times$10$^{-1}$$\pm$6.00$\times$10$^{-2}$ & -                        & 1.0                   & 2.0$\times$10$^{-2}$   & 0.028                 & 0.064  & 4.64   \\
1250 & DIRBE       & 7.04$\times$10$^{-2}$$\pm$1.19$\times$10$^{-1}$ & -                        & 2.05                  & 4.10$\times$10$^{-2}$  & 0.42                  & 0.10   & 42     \\
2141 & DIRBE       & 9.94$\times$10$^{-2}$$\pm$1.53$\times$10$^{-1}$ & -                        & 2.65                  & 5.29$\times$10$^{-2}$  & 0.79                  & 0.10   & 42     \\
3000 & DIRBE/\IRAS & 0.0$\pm$4.3$\times$10$^{-2}$                    & -                        & 1.30                  & 2.60$\times$10$^{-2}$  & 0.06                  & 0.10   & \ 6.1
\enddata
\end{deluxetable*}
\end{center}
